---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## Tracking Instagram advertisements

This dynamic report tracks the Instagram advertisements that I observed over time.
The data were collected by recording one advertisement each time I saw one on my feed.
The report shows some simple patterns in the ads, including ad type and time of day.

```{r}
library(tidyverse)

csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQ_kRGyH9Is_Uwzt417-nD8hmIJkJWO9jcjgTGdleAx_35xXpG04sQwWUz98qfz3TcnR-rlGoQMJGYr/pub?output=csv"

logged_data <- read_csv(csv_url)

latest_data <- logged_data %>%
  rename(ad_type = 2,
         duration_seconds = 3,
         discount_offer = 4,
         time_of_day = 5,
         ad_format = 6
         )
```
### Summary

A total of `r nrow(latest_data)` Instagram advertisements were recorded.

The average ad length was `r round(mean(latest_data$duration_seconds, na.rm = TRUE), 1)` seconds.

### Ad types
```{r}
latest_data %>%
  ggplot() +
    geom_bar(aes(x = ad_type), fill = "blue") +
  labs(title = "Number of Instagram ads by type",
       x = "Ad type",
       y = "Number of ads")
```

### Time of day
```{r}
latest_data %>%
  ggplot() +
    geom_bar(aes(x = time_of_day), fill = "pink") +
  labs(title = "Number of Instagram ads by time of day",
       x = "Time of day",
       y = "Number of ads")
```